Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics

### 2020-08-12 infiniteci.tex

>>>>

%% almost as usual
\author{Matthias Templ\\ Vienna University of Technology \And 
        Second Author\\ Affiliation}
%% \AND can be used instead of \And and starts a new line
\title{Guidelines for Submitting a Manuscript to the Austrian Journal of Statistics}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Templ, Second Author} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
\Shorttitle{A Capitalized Title} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  This guideline of the Austrian Journal of Statistics (AJS) shows the required style of manuscripts submitted to the Austrian Journal of Statistics. We highly recommend
to follow exactly the provided instructions already at the very
beginning when writing the paper. The present document can be used
directly as template. The file named {\tt guidelinesAJS.tex} may be
obtained from the site \href{https://github.com/matthias-da/ajs-public}{https://github.com/matthias-da/ajs-public}.

Manuscripts submitted without considering the AJS style file will be very likely not sent into review, but declined with possibility for re-submission.
}
\Keywords{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}
\Plainkeyword{meta-analysis, confidence intervals,file-drawer problem, publication bias, selection models,weigth function models}

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{2012-06-04}
%% \Acceptdate{2012-06-04}
%% \setcounter{page}{1}
\Pages{1--xx}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Matthias Templ\\
  Institue of Data Analysis and Process Design\\
  Zurich University of Applied Sciences\\
  CH-8400 Winterthur, Switzerland\\
  E-mail: \email{matthias.templ@gmail.com}\\
  URL: \url{https://www.zhaw.ch/de/ueber-uns/person/teml/}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
